Weather Data Integration and Assimilation System\\

### 2020-02-15 introduction/sec_1-motivation.tex
Grammarly: Chapter 1

Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water. The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input. For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the correct model is selected. After removing the bias, the extract information is then fed into another set of models/simulators. 
As an example, FLO2D is a hydrologic model that can use to predict the surface water level. A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from \acrshort{nwm} model to forecast future water levels.
\dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
\dbc{cite both NWM and WRF}
\gkc{FIXED BOTH}

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing its own system with the idea of long-term maintainability rather depend on existing weather data integration systems. It collected real-time data from weather stations and other government entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

Processed weather data needs to be accessed by many third-party applications and research in order to make use of them. For example, logistic companies could use those data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers in advance, as well as calculate premiums based on anticipated weather patterns. Also farmers rely on weather forecasts to decide what work to do on any particular day. For example, drying hay is only feasible in dry weather. Further the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential, since prior to takeoff on the conditions to expect en route and at their destination. 
Thus it is required a platform to provide such 3rd party access, and use the data or process those based on their applications.

While Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ARCHITECTUREP2.39} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than those software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the data flow. In such a cases, it required to get the support from the vendor in order to integrate and configure the system.
And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. \acrfull{wdias} uses the modern architecture pattern such as microservice in order to achieve scalability, rather using monolithic architecture or client service architecture. Most existing systems required to shutdown in order to update the system configuration such as \acrshort{fews}, but a systems which is access by many third parties should be operate 99.9\% without any downtime and should allows to add new features on the fly with rollover capabilities. The proposed system should be independent of the platform. But most software out there is not, as example \acrshort{fews} can run on Windows and Linux. And should be independent underline infrastructure providers which give much flexibility for the users to decide the best cost effective way to host it. Given the above facts, there is a necessary for such a systems to be implemented.

>>>>

Weather prediction is essential to reduce impact due to natural disasters and to gain effectively manage natural resources like water. The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the input. For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the correct model is selected. After removing the bias, the extract information is then fed into another set of models/simulators. 
As an example, FLO2D is a hydrologic model that can use to predict the surface water level. A given FLO2D model can simulate with the initial surface water levels and the sequence of forecasted rainfall for the corresponding modeled area from the \acrshort{nwm} model to forecast future water levels.
\dbc{Highighted part doesn't make much sense to me. Need to be reworded.}
\dbc{cite both NWM and WRF}
\gkc{FIXED BOTH}

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing its system with the idea of long-term maintainability rather depend on existing weather data integration systems. It collected real-time data from weather stations and other government entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, mitigation, and management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

Processed weather data needs to be accessed by many third-party applications and research to make use of them. For example, logistics companies could use those data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns. Also, farmers rely on weather forecasts to decide what work to do on any particular day. For example, drying hay is only feasible in dry weather. Further, the aviation industry is especially sensitive to the weather, accurate weather forecasting is essential since before takeoff on the conditions to expect en route and at their destination. 
Thus it is required a platform to provide such 3rd party access, and use the data or process those based on their applications.

While Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ARCHITECTUREP2.39} are some of well-known Weather Data Integration and Assimilation (WDIA) systems, they are proprietary. Further \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source.
Even though there are many data integration systems, most of them are proprietary or closed source. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. As an example, \acrshort{fews} does not support FLO2D model integration, and \acrshort{curw} is using FLO2D for water level forecasting in the data flow. In such a case, it required to get support from the vendor to integrate and configure the system.
And most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. \acrfull{wdias} uses the modern architecture pattern such as microservice to achieve scalability, rather using monolithic architecture or client service architecture. Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities. The proposed system should be independent of the platform. But most software out there is not, as an example \acrshort{fews} can run on Windows and Linux. And should be independent underline infrastructure providers which gives much flexibility for the users to decide the best cost-effective way to host it. Given the above facts, there is a necessity for such a system to be implemented.

### 2020-02-15 introduction/sec_2-problem_and_objectives.tex
Grammarly: Chapter 1

\section{Problem Statement}
Handling spatio-temporal weather data is challenging \db{as ...}. Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data. Furthermore, it should support geographical and time-base queries, as well as provide third-party access to data with easy integration. Scalability and high availability are also essential to support different use cases and mission-critical nature of applications. Therefore, we need an extendable system to support weather models by efficiently ingesting, storing, and retrieving data. In this context, the research problem can be stated as follows:

\emph{design and implement an extendable weather data integration, assimilation and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies}
\dbc{Give a proper problem statement.}
\gkc{UPDATED. Looked into the OneNote samples. I  should follow one of them from the beginning. :( }

\section{Objectives}
We address above problem statement by achieving the following research objectives:
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API for third-party data sharing
%    \item To use open source tools and provide the source publicly with appropriate liecense.
\end{itemize}

>>>>

\section{Problem Statement}
Handling Spatio-temporal weather data is challenging \dbc{as} it involves large data volumes required to have a higher number of resources such as computation, storage, and network bandwidth. Moreover, the data integration system needs to be capable of interacting with different data formats including Spatio-temporal bulk stream data. Furthermore, it should support geographical and time-based queries, as well as provide third-party access to data with easy integration. Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
And users should be able to easily deploy and manage the system with modern technologies and should be able to get the advantage of technology advancement. In this context, the research problem can be stated as follows:

\emph{Design and implement an extendable weather data integration, assimilation, and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.}
\dbc{Give a proper problem statement.}
\gkc{UPDATED. Looked into the OneNote samples. I  should follow one of them from the beginning. :( }

\section{Objectives}
We address the above problem statement by achieving the following research objectives:
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API for third-party data sharing
%    \item To use open source tools and provide the source publicly with appropriate liecense.
\end{itemize}

### 2020-02-15 introduction/sec_3-outline.tex
Grammarly: Chapter 1

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in \cref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides details about how the \acrshort{wdias} is design by following a microservice architecture and the date preprocessing capabilities of the system. Performance analysis is presented in Chapter \ref{ch:results}. Here we discuss experiment setup of the \acrshort{wdias} and analyze the observations with respect to performance metrics. Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed about the research limitations and future work.

>>>>

\section{Outline}
The rest of the thesis is organized as follows. The literature review is presented in \cref{ch:literature}, and discuss the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides details about how the \acrshort{wdias} is designed by following a microservice architecture and the date preprocessing capabilities of the system. Performance analysis is presented in Chapter \ref{ch:results}. Here we discuss the experimental setup of the \acrshort{wdias} and analyze the observations concerning performance metrics. Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed the research limitations and future work.
